### 2013-06-23 trunk/network-science/paper.tex
7

Centrality, usually defined on vertices, is frequently used to measure the
importance of a specific node in graphs of all kinds. There are many previous
studies about the static graph centralities[?], and there are many useful
network analysis algorithms that used some kind of graph centralities. However,
most social networks change over time, and even more unfortunately, some of the
networks are large-scaled, which could make the analysis become hard and
costly, hence limit the scale of meaningful data mining. Moreover, the time
effect can also become a factor of the centrality, that is, the same graph with
different evolving sequence may have totally different metrics. On an
intuitive level, the node connected with more higher activity nodes should be
more important at that time, even if other node have much more silent
neighbors. If we do not excavate the information on the time dimension, we will
lose tremendous information and also the possibility of accumulative
computation which could be helpful in enhancement the speed of answering
consistent quering.

@@

@@

\subsection{Desiderata}
% TODO
\subsection{Design and Analysis}
% TODO
\section{Algorithms}
% TODO
\subsection{Maintaining the basic graph structure}
% TODO
\subsection{Historical Queries}
% TODO
\subsection{Computing Metrics}
% TODO
\subsection{Mining Significant Data}
% TODO
\subsection{Optimization and Parallelizability}
% TODO
\section{Experiment}
% TODO
\section{Conclusion and Perspective}
% TODO
\nocite{*}
\bibliography{paper.bib}
\end{document}

>>>>

Centrality, usually defined on vertices, is frequently used to measure the
importance of a specific node in graphs of all kinds. There are many previous
studies about the static graph centralities[?], such as page rank
algorithm\cite{page1999pagerank}, and there are many useful
network analysis algorithms that used some kind of graph centralities. However,
most social networks change over time, and even more unfortunately, some of the
networks are large-scaled, which could make the analysis become hard and
costly, hence limit the scale of meaningful data mining. Moreover, the time
effect can also become a factor of the centrality, that is, the same graph with
different evolving sequence may have totally different metrics. On an
intuitive level, the node connected with more higher activity nodes should be
more important at that time, even if other node have much more silent
neighbors. If we do not excavate the information on the time dimension, we will
lose tremendous information and also the possibility of accumulative
computation which could be helpful in enhancement the speed of answering
consistent quering.

@@

The clustering coefficient[?], namely
\begin{equation}
c.c=\frac{\#\text{closed paths of len 2}}{\#\text{paths of len 2}},
\end{equation}
for a typical social network is a possitive
number, which means people are more willing to make interactions with close
related people than unfamiliars.

@@

\subsection{Desiderata}
Suppose $Act(G_t,v)$ returns the activity of node $v$ in the evolving graph in
time $t$. Then $Act(G_t,v)$ should be a deterministic function of $v$ and
$E_t$.
\begin{itemize}
\item \textbf{normalization}:

We want the metrics to derive other functions, so it will be nice if we can
limit the range of the function.
\begin{equation}
0\leq Act(G_t,v) \leq 1.
\end{equation}

\item \textbf{initialization}:

A node with no neighbors is totally inactive.
\begin{equation}
k(G_t,v)=0\implies Act(G_t,v)=0.
\end{equation}

\item \textbf{monotonicity}:

If a vertex $v$ performs an interaction $(v,u)$ at time $t$, and suppose the
interaction is the only change to the graph at time $t$, then the activity of
$v$ should enhance.

\begin{equation}
E_{t+1}=E_t\cup\{e(u,v,t,w)\}\implies Act(G_{t+1},v)>Act(G_{t},v).
\end{equation}

\item \textbf{attenuation}:

If the network keeps silent, the activity metric of any node $v$ should be decreasing
over time by intuition. Because there is a lower bound for activity and we want
the attenuation process to be infinity long since a node changed the network
once in past time is potential to make another. So we make the decay rate
of activity for silent nodes to be also decreasing. However in our pure growing
model, the change of network structure must happen at integral time. So we
expand the definition
\begin{equation}
G_t=G_{\lfloor t \rfloor}\text{ and } E_t=E_{\lfloor t \rfloor},
\end{equation}
to make $Act(G,v)$ a well defined $\mathbb{R}\to [0,1]$ function.

\begin{equation}

\end{equation}

\end{itemize}
\subsection{Design and Analysis}
% TODO
\section{Algorithms}
% TODO
\subsection{Maintaining the basic graph structure}
% TODO
\subsection{Historical Queries}
% TODO
\subsection{Computing Metrics}
% TODO
\subsection{Mining Significant Data}
% TODO
\subsection{Optimization and Parallelizability}
% TODO
\section{Experiment}
% TODO
\section{Conclusion and Perspective}
% TODO
\nocite{*}
\bibliography{paper.bib}
\end{document}
